### 2011-05-11 paper.tex
finished intersection lemma

By assumption, $C$ is closed under majority reductions and under intersection. Thus,\linebreak $\intersect(\majority(M)) \in C$. We want to show that $\intersect(L) \in \bp\cdot C$. For any $(x_1,x_2,...,x_k)$, we randomly choose random strings $y_{i,j}$ of length $p(|x_i|)$, for $1\le i\le k$ and $j\le 1\le \ell$, where $\ell = \lceil 48\ln(3/2)k \rceil$. Then, we check if
\begin{center}
$((x_{1,1},x_{1,2},...,x_{1,\ell}),(x_{2,1},x_{2,2},...,x_{2,\ell}),...,(x_{k,1},x_{k,2},...,x_{k,\ell}))$
\end{center}
is in $\intersect(\majority(\ell))$.

>>>>

By assumption, $C$ is closed under majority reductions and under intersection. Thus,\linebreak $\intersect(\majority(M)) \in C$. We want to show that $\intersect(L) \in \bp\cdot C$. For any $(x_1,x_2,...,x_k)$, we randomly choose random strings $y_{i,j}$ of length $p(|x_i|)$, for $1\le i\le k$ and $j\le 1\le \ell$, where $\ell = \lceil -48\ln(1 - (2/3)^{1/k}) \rceil$. Then, we check if $(X_1, X_2, ..., X_k)$
is in $\intersect(\majority(M))$, where
\begin{center}
$X_i = ((x_i,y_{i,1}),(x_{i},y_{i,2}),...,(x_{i},y_{i,\ell}))$.
\end{center}
By the Chernoff bound, as in the proof of Lemma \ref{majorityimpliesamplify}, we have that $X_i$ is in $\majority(M)$ with probability greater than $e^{-(1/4)^2 (2\ell/3)/2} \ge 1 - (2/3)^{1/k}$ if $x_i \in L$. If $x_i \in L$ for all $i$, then the probability that there exists some $i$ for which $X_i$ is not in $\majority(M)$ is therefore greater than $((2/3)^{1/k})^k = 2/3$. If there is some $i$ for which $x_i \not\in L$, then there is a $1 - (2/3)^{1/k} \ge 2/3$ chance that $X_i \not \in \majority(M)$.

Thus, we get that $(X_1,...,X_k)\in\intersect(\majority(M))$ with probability greater than $2/3$ if $(x_1,x_2,...,x_k)\in L$, and $(X_1,...,X_k)\not\in\intersect(\majority(M))$ with probability greater than $2/3$ if $(x_1,x_2,...,x_k)\not\in L$. Therefore, $\intersect(L) \in \bp \cdot C$, so $\bp \cdot C$ is closed under intersection.
